---
title: "clus_explorer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{clus_explorer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Modular Structure
The CLUS Explorer app is initiated using `{golem}` package.

This facilitates the following:

- The app code and data are organized like a package. This means that all
files in `/R` directory and all data objects in `/data` directory are automatically
loaded into memory when the application is started.
- The app can easily be organized into modules, making it easier to maintain and 
understand the architecuture.

The application is highly modularized, with each module being created in a separate file,
and each file containing both `ui` and `server` Shiny functions. 

All files containing the application logic are in `/R` directory.

For easier organization, the "page" modules are prefixed with `mod_page_` prefix, 
while reusable chart modules are prefixed with `mod_chart_` prefix. 

There are also several files containing helper functions. They all contain `_utils_`
in the file name.

## Running the App and App Hierarchy

The app is started by running the `/app.R` file in the repo root. It calls the `golem::run_dev` 
function which loads the `app_ui` and `app_server` files, which in turn load Shiny `ui` 
and `server` functions.

Following is the hierarchy of the modules:

`app.ui` - defines the Shiny Dashboard page, sidebar menu and tab items

Tab items call the following UI modules:

- mod_page_home_ui
- mod_page_scenarios_ui
- mod_page_dashboard_summary_ui
- mod_page_dashboard_caribou_ui
- mod_page_dashboard_forestry_ui
- mod_page_dashboard_fire_ui
- mod_page_dashboard_fisher_ui
- mod_page_dashboard_grizzly_ui
- mod_page_report_ui

passing in the module ID as a string.

`app_server` - Calls the following modules

- mod_page_home_server
- mod_page_scenarios_server

It observes the changes in selected scenarios and recalculates `reportList`
reactive value, which contains all data relevant for generating charts and reports.

The server functions of remaining modules are invoked by passing in the `reportList`
reactive value.

- mod_page_dashboard_summary_server
- mod_page_dashboard_caribou_server
- mod_page_dashboard_grizzly_server
- mod_page_dashboard_forestry_server
- mod_page_dashboard_fisher_server
- mod_page_dashboard_fire_server

The report generation module `mod_page_report_server` is called by passing in 
`reportList` reactive and a number of additional relevant variables required to generate the PDF, Word or
PowerPoint reports.

## Generating reports

The app can generate reports in PDF and Microsoft Word or PowerPoint formats. 
The prerequisites for generating the report are:

- Selecting the area of interest and scenarios on the Scenarios page.
- Baseline scenario on the Dashboard - Summary page.
- At least one section on the Generate Report page.

When the "Download report" button is clicked, the download handler function takes 
all the relevant data objects that were passed in to the `mod_page_report` module 
as parameters, and passes them as `params` list into the `rmarkdown::render` function.

The rendering uses `inst/app/report.Rmd` markdown file as a template. The `report.Rmd` file
accepts all parameters in `params` key of the `yaml` front matter.

In the `yaml` front matter, it also sets `latex` and other variables used for rendering
and loads the required R packages.

Since generating the report allows the user to select the sections they want included,
rendering is also broken down into individual markdown files for each of the sections.

The evaluation of user selection which sections should be included, and inclusion of 
individual markdown files corresponding to user selection happens in the code chunk 
definitions in `inst/app/report.Rmd' markdown file. For example:

```{r eval=FALSE}
<!-- Summary -->
{r, eval=('summary' %in% params$details), child=c('reports/summary.Rmd')}
```

These included individual markdown files run in the same environment as the main 
`report.Rmd` file, so all variables and data objects are available for them at runtime.

## Managing Dependencies

The app uses `{renv}` package to manage dependencies and package versions. When the 
containers are started, the first command that is executed is `renv::restore()`,
which brings the environment up to date with the packages and versions
recorded in `renv.lock` file in the repository root.
